The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-04 dit-paper_ieee.tex
no idea
Small changes from Joël Goossens's remarks

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$
			\item $H = \operatorname{lcm}(T_1, \cdots, T_{n})$
			\item $O_{max} = \max (O_1, \cdots, O_{n})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			\emph{strictly} before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval between two consecutive idle times in
			which at least one job is executing.
			\item The interval between the initial time ($t=0$) and the first
			idle time is called the \emph{first busy period}.
		\end{itemize}

@@

	We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms}, based on the demand-bound function.

@@

	Mathematically,
	\[
		\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
	\]
	where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
	and deadlines are both in the closed interval $[t_1, t_2]$.

@@

  Even then, the number of constraints to consider is exponential in the number
  of tasks. While it has been shown that constraints that cover intervals ending
  after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
  therefore not usable for the purposes of this paper. The
  following concept, initially described by \cite{lipariaverage}, is thus introduced. It is similar to the end of the busy period but does not depend on the execution times.

@@

  For synchronous systems in which the execution times are not known, the first DIT $t_d$
  is our ``best guess'' at an upper limit on the end of the busy period. As it was sufficient
  to check the DBF test in intervals $[0, t]$ before the end of the busy period, it is
  slightly more pessimistic but still correct to use the following condition:
  \[
  	\begin{array}{c}
  		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d \\
  		\iff \text{The system is feasible}
  	\end{array}
  \]

>>>>

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$
			\item $H = \operatorname{lcm}(T_1, \cdots, T_{n})$
			\item $O_{max} = \max (O_1, \cdots, O_{n})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			\emph{strictly} before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval between two consecutive idle times in
			which at least one job is executing.
			\item The interval between the initial time ($t=0$) and the first
			idle time after $t=0$ is called the \emph{first busy period}.
		\end{itemize}

@@

	We recall the necessary and sufficient feasability condition on monoprocessor platform given in \cite{baruah1999generalized, baruah1990algorithms} and based on the demand-bound function.

@@

	Mathematically,
	\[
		\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
	\]
	where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ which arrival times
	and deadlines are both in the closed interval $[t_1, t_2]$.

@@

  Even then, the number of constraints to consider is exponential in the number
  of tasks. While it has been shown that constraints that cover intervals ending
  after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
  therefore not usable for the purposes of this paper. The
  following concept, initially described by \cite{lipariaverage}, is thus introduced. It gives an upper bound for to the end of the busy period and does not depend on the execution times.

@@

  For synchronous systems in which the execution times are not known, the first DIT $t_d$
  is our ``best guess'' at an upper limit on the end of the busy period. As it was sufficient
  to check the DBF test in intervals $[0, t]$ before the end of the busy period, it is
  slightly more pessimistic but still correct to use the following condition:
  \[
  		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d
  		\iff \text{The system is feasible}
  \]
